Radioastronomical image reconstruction using Kalman filter under ionospheric perturbations

### 2022-08-01 article/article.tex
art update

\renewcommand{\expval}[1]{\text{E}\left[#1\right]}
\newcommand{\w}{\boldsymbol{w}}
\renewcommand{\v}{\boldsymbol{v}}
\newcommand{\Q}{\boldsymbol{\mathsf{Q}}}
\newcommand{\R}{\boldsymbol{\mathsf{R}}}
\renewcommand{\H}{\boldsymbol{\mathsf{H}}}
\newcommand{\A}{\boldsymbol{\mathsf{A}}}
\newcommand{\I}{\boldsymbol{\mathsf{I}}}

@@

	When a 2-D matrix element is indexed with a single coordinate, it designates the reshaped matrix in a 1-D vector.

@@

	Kalman filtering works in 2 steps :
	\paragraph{Prediction} : This step predicts the state of the system at next time-step through de transition-state model, and the predicted measurement :
	$$
	\begin{cases}
		\xp = A\xa + \moy{\w_k}\\
		\yp = H\xp + \moy{\v_k}
	\end{cases}
	$$
	And the covariance matrix :
	$$
		\Pp = \autocorr{\xp - \x_k} = H\Pa H^H + \Q_k
	$$
	This result can be computed using least-square estimation of the prediction error covariance\cite{intro_KF}

@@

>>>>

\renewcommand{\expval}[1]{\text{E}\left[#1\right]}
\newcommand{\w}{\boldsymbol{w}}
\renewcommand{\v}{\boldsymbol{v}}
\newcommand{\Q}{\boldsymbol{\mathsf{Q}}}
\newcommand{\R}{\boldsymbol{\mathsf{R}}}
\renewcommand{\H}{\boldsymbol{\mathsf{H}}}
\newcommand{\A}{\boldsymbol{\mathsf{A}}}
\newcommand{\I}{\boldsymbol{\mathsf{I}}}
\newcommand{\K}{\boldsymbol{\mathsf{K}}}

@@

	When a 2-D matrix element is indexed with a single coordinate, it designates the reshaped matrix in a 1-D vector.\\

	$\mathbb{I}$ is the identity matrix.

@@

	Kalman filtering works in 2 steps :
	\paragraph{Prediction} : This step predicts the state of the system at next time-step through de transition-state model, and the predicted measurement :
	$$
	\begin{cases}
		\xp = A\xa + \moy{\w_k}\\
		\yp = H\xp + \moy{\v_k}
	\end{cases}
	$$
	And the covariance matrix :
	$$
		\Pp = \autocorr{\xp - \x_k} = \A\Pa \A^H + \Q_k
	$$
	This result can be computed using least-square estimation of the prediction error covariance\cite{intro_KF}

@@

	By the same calculation than before \cite{intro_KF}, position error being decorrelated with other errors or noise, the equations become :
	\begin{subequations}
		\begin{equation}\label{xpe}
			\xp^* = \A\xa + \moy{\w_k}
		\end{equation}\begin{equation}
			\yp^* = \H^*\xp^* + \moy{\v_k}
		\end{equation}\begin{equation}
			\Pp^* = \A\Pa^*\A^H + \Q_k
		\end{equation}\begin{equation}
			\K_k^* = \Pp^*\left(\H^*\right)^H\left(\H^*\Pp^*\left(\H^*\right)^H\right)^{-1}
		\end{equation}\begin{equation}
			\Pe^* = \Pp^* + \K_k^*\H^*\Pp^*\left(\H^*\right)^H\left(\K_k^*\right)^H + \K_k^*\R_k\left(\K_k^*\right)^H
		\end{equation}\begin{equation}
			\xe^* = \xp^* + \K_k^*(\y_k - \yp^*)
		\end{equation}
	\end{subequations}

	To evaluate reconstruction quality, we can introduce the following errors :
	\begin{equation}
		\vbeps^{\K}_k = \K_k^* - \K_k
	\end{equation}
	\begin{equation}\label{errX}
		\vbeps^{\x}_k = \xe^* - \xe
	\end{equation}

	Respectively gain error and estimation error.\\
	Using equation (\ref{xpe}), (\ref{errX}) can be rewritten :
	\begin{equation}
		\vbeps^{\x}_k = \vbeps^{\K}_k\y_k + \left(\mathbb{I} - \K_k^*\H^*\right)\xp^* - \left(\mathbb{I} - \K_k\H\right)\xp
	\end{equation}

	To evaluate the reconstruction error evolution
